linearGR_Models

### 2018-06-01 manuscriptAnalysis/linearGR_ModelsMap_BKT.Rmd
after model selection

d <- d2 %>% filter(
  #  species == as.numeric(speciesInGr),
    !is.na(grLength),
    !is.na(countPStd) #removes 5 obs
  )

@@

```{r}
# -2.5 values are mostly from season==2 and isYOY==1
ggplot(d, aes(sampleNumber,cBKTStd)) + geom_point() + geom_line() + facet_grid(season~river)
ggplot(d, aes(sampleNumber,cBNTStd)) + geom_point() + geom_line() + facet_grid(season~river)
ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_grid(season~river)

ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_wrap(~river)

@@

ggplot(d, aes(sampleNumber,grLength)) + geom_point()  + facet_grid(species~river+season)

ggplot(d, aes(cBKTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
ggplot(d, aes(cBNTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
ggplot(d, aes(cATSStd,grLength)) + geom_point()  + facet_grid(species~river+season)

@@

```{r}
pairs(d[,c('countPStd','countPStdBKT_01','countPStdBNT_01','countPStdATS_01')])
pairs(d[,c('countPBKT','countPBNT','countPATS')])
pairs(d[,c('cBKTStd','cBNTStd','cATSStd','tempStd','flowStd')])
pairs(d[,c('tempStd2','flowStd2','tempStd','flowStd')])
d20 <- d
d20[d20 == -2.5] <- NA
pairs(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')])
round(cor(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')], use="complete.obs"),2)
```

@@

mod[[1]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   (1|ind), data = df ) }

mod[[2]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd + 
                   lengthByYear  +
                   (1|ind), data = df ) }

mod[[3]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   (1|ind), data = df ) } 
# 3 is better for bkt

# need squared term for flow or temp?
mod[[4]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * tempStd2 + 
                   isYOY * river * season * flowStd2  +
                   (1|ind), data = df ) }

mod[[5]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * tempStd2 * flowStd2  +
                   (1|ind), data = df ) }

mod[[6]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * tempStd2 + 
                   (1|ind), data = df ) }

mod[[7]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * flowStd2  +
                   (1|ind), data = df ) } 
# 3 is best for bkt, bnt
# 5 is best for ATS
```
        rowname  df       AIC     rowname.1 df.1     AIC.1     rowname.2 df.2     AIC.2
1 o$model3[[1]] 132 -24138.75 o$model3[[2]]   60 -11185.96 o$model5[[3]]   53 -27273.26
2 o$model1[[1]] 130 -24066.23 o$model7[[2]]   74 -11185.65 o$model4[[3]]   46 -27271.94
3 o$model2[[1]] 131 -24051.02 o$model6[[2]]   74 -11140.56 o$model7[[3]]   39 -26891.76
4 o$model6[[1]] 164 -24031.80 o$model4[[2]]   88 -11113.99 o$model6[[3]]   39 -26866.52
5 o$model5[[1]] 226 -23972.19 o$model1[[2]]   58 -11093.02 o$model3[[3]]   32 -26711.17
6 o$model7[[1]] 164 -23945.62 o$model2[[2]]   59 -11076.95 o$model1[[3]]   30 -26675.04
7 o$model4[[1]] 196 -23919.37 o$model5[[2]]  102 -11021.51 o$model2[[3]]   31 -26664.86

@@

mod[[8]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   isYOY * season * cBKTStd +
                   (1|ind), data = df ) }

mod[[9]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   isYOY * season * cBNTStd +
                   (1|ind), data = df ) }

mod[[10]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * lengthByYear  +
                   isYOY *         season * cATSStd +
                   (1|ind), data = df ) }

mod[[11]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * lengthByYear  +
                  isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY *         season * cATSStd +
                  (1|ind), data = df ) }

mod[[12]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
                   (1|ind), data = df ) }

mod[[13]] <- function(df) {
  print(c('mod = 13' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear +
                   isYOY * season * cBKTStd * cBNTStd +
                   (1|ind), data = df ) } 
```

1  o$model11[[1]] 196 -24757.35 o$model13[[2]]   81 -11300.64 o$model12[[3]]   81 -29435.49
2   o$model8[[1]] 140 -24427.44  o$model9[[2]]   67 -11258.70 o$model11[[3]]   53 -28160.01
3  o$model13[[1]] 156 -24407.24  o$model8[[2]]   67 -11227.08 o$model13[[3]]   53 -27792.61
4  o$model12[[1]] 188 -24354.95 o$model11[[2]]   95 -11217.75  o$model8[[3]]   39 -27393.12
5   o$model3[[1]] 132 -24138.75 o$model10[[2]]   67 -11204.81  o$model5[[3]]   53 -27273.26
6   o$model9[[1]] 140 -24119.50  o$model3[[2]]   60 -11185.96  o$model4[[3]]   46 -27271.94
7  o$model10[[1]] 140 -24084.14  o$model7[[2]]   74 -11185.65  o$model9[[3]]   39 -26895.35
8   o$model1[[1]] 130 -24066.23 o$model12[[2]]  109 -11148.99  o$model7[[3]]   39 -26891.76
9   o$model2[[1]] 131 -24051.02  o$model6[[2]]   74 -11140.56  o$model6[[3]]   39 -26866.52
10  o$model6[[1]] 164 -24031.80  o$model4[[2]]   88 -11113.99 o$model10[[3]]   39 -26735.14
11  o$model5[[1]] 226 -23972.19  o$model1[[2]]   58 -11093.02  o$model3[[3]]   32 -26711.17
12  o$model7[[1]] 164 -23945.62  o$model2[[2]]   59 -11076.95  o$model1[[3]]   30 -26675.04
13  o$model4[[1]] 196 -23919.37  o$model5[[2]]  102 -11021.51  o$model2[[3]]   31 -26664.86 
```{r}
mod[[14]] <- function(df) {
    print(c('mod = 14' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd * tempStd * flowStd +
                   isYOY * river * season * cBNTStd * tempStd * flowStd +
                   isYOY *         season * cATSStd * tempStd * flowStd +

mod[[15]] <- function(df) {
    print(c('mod = 15' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd * tempStd +
                   isYOY * river * season * cBNTStd * tempStd +
                   isYOY *         season * cATSStd * tempStd +
                   isYOY * river * season * cBKTStd * flowStd +
                   isYOY * river * season * cBNTStd * flowStd +
                   isYOY *         season * cATSStd * flowStd +

mod[[16]] <- function(df) {
    print(c('mod = 16' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd * tempStd +
                   isYOY * river * season * cBNTStd * tempStd +
                   isYOY *         season * cATSStd * tempStd +
                   (1|ind), data = df ) }

mod[[17]] <- function(df) {
    print(c('mod = 17' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd * flowStd +
                   isYOY * river * season * cBNTStd * flowStd +
                   isYOY *         season * cATSStd * flowStd +
                   (1|ind), data = df ) }

mod[[18]] <- function(df) {
    print(c('mod = 18' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd * ATS01DATA +
                   (1|ind), data = df ) }
```

1  o$model11[[1]] 196 -24757.35 o$model13[[2]]   81 -11300.64 o$model12[[3]]   81 -29435.49
2  o$model16[[1]] 258 -24687.75  o$model9[[2]]   67 -11258.70 o$model14[[3]]  116 -29023.66
3  o$model14[[1]] 378 -24667.16  o$model8[[2]]   67 -11227.08 o$model15[[3]]   95 -28852.96
4  o$model17[[1]] 258 -24658.77 o$model11[[2]]   95 -11217.75 o$model16[[3]]   74 -28765.54
5  o$model15[[1]] 319 -24637.70 o$model10[[2]]   67 -11204.81 o$model17[[3]]   74 -28385.96
6   o$model8[[1]] 140 -24427.44  o$model3[[2]]   60 -11185.96 o$model11[[3]]   53 -28160.01
7  o$model13[[1]] 156 -24407.24  o$model7[[2]]   74 -11185.65 o$model13[[3]]   53 -27792.61
8  o$model18[[1]] 164 -24402.75 o$model17[[2]]  130 -11178.95 o$model18[[3]]   53 -27529.84
9  o$model12[[1]] 188 -24354.95 o$model18[[2]]   88 -11160.65  o$model8[[3]]   39 -27393.12
10  o$model3[[1]] 132 -24138.75 o$model12[[2]]  109 -11148.99  o$model5[[3]]   53 -27273.26
11  o$model9[[1]] 140 -24119.50  o$model6[[2]]   74 -11140.56  o$model4[[3]]   46 -27271.94
12 o$model10[[1]] 140 -24084.14  o$model4[[2]]   88 -11113.99  o$model9[[3]]   39 -26895.35
13  o$model1[[1]] 130 -24066.23  o$model1[[2]]   58 -11093.02  o$model7[[3]]   39 -26891.76
14  o$model2[[1]] 131 -24051.02 o$model16[[2]]  130 -11088.10  o$model6[[3]]   39 -26866.52
15  o$model6[[1]] 164 -24031.80  o$model2[[2]]   59 -11076.95 o$model10[[3]]   39 -26735.14
16  o$model5[[1]] 226 -23972.19 o$model15[[2]]  164 -11076.43  o$model3[[3]]   32 -26711.17
17  o$model7[[1]] 164 -23945.62  o$model5[[2]]  102 -11021.51  o$model1[[3]]   30 -26675.04
18  o$model4[[1]] 196 -23919.37 o$model14[[2]]  196 -11020.01  o$model2[[3]]   31 -26664.86

@@

mod[[19]] <- function(df) {
    print(c('mod = 19' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * lengthByYear  +
                   isYOY * river * season * cBKTStd * lengthByYear +
                   isYOY * river * season * cBNTStd * lengthByYear +
                   isYOY *         season * cATSStd * lengthByYear  +

mod[[20]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * lengthByYear  +
                  isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY *         season * cATSStd +
                  isYOY * river * season * tempStd^2  +
                  isYOY * river * season * flowStd^2  +
                  (1|ind), data = df ) }

>>>>

d <- d2 %>% filter( !is.na(grLength) )

d <- d %>% filter(
 !is.na(countPStd) #removes 5 obs
  )

@@

```{r}
# -2.5 values are mostly from season==2 and isYOY==1
# ggplot(d, aes(sampleNumber,cBKTStd)) + geom_point() + geom_line() + facet_grid(season~river)
# ggplot(d, aes(sampleNumber,cBNTStd)) + geom_point() + geom_line() + facet_grid(season~river)
# ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_grid(season~river)
# 
# ggplot(d, aes(sampleNumber,cATSStd)) + geom_point() + geom_line() + facet_wrap(~river)

@@

# ggplot(d, aes(sampleNumber,grLength)) + geom_point()  + facet_grid(species~river+season)
# 
# ggplot(d, aes(cBKTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
# ggplot(d, aes(cBNTStd,grLength)) + geom_point()  + facet_grid(species~river+season)
# ggplot(d, aes(cATSStd,grLength)) + geom_point()  + facet_grid(species~river+season)

@@

```{r}
# pairs(d[,c('countPStd','countPStdBKT_01','countPStdBNT_01','countPStdATS_01')])
# pairs(d[,c('countPBKT','countPBNT','countPATS')])
# pairs(d[,c('cBKTStd','cBNTStd','cATSStd','tempStd','flowStd')])
# pairs(d[,c('tempStd2','flowStd2','tempStd','flowStd')])
# d20 <- d
# d20[d20 == -2.5] <- NA
# pairs(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')])
# round(cor(d20[,c('countPStd','countPStdBKT','countPStdBNT','countPStdATS')], use="complete.obs"),2)
```

@@

# need length? NO
mod[[1]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   (1|ind) + (1|season), data = df ) }

mod[[2]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd + 
                   lengthByYear  +
                   (1|ind) + (1|season), data = df ) } 
```

        rowname  df       AIC     rowname.1 df.1     AIC.1     rowname.2 df.2     AIC.2
1 o$model1[[1]] 131 -24064.23 o$model1[[2]]   59 -11091.02 o$model1[[3]]   31 -26673.04
2 o$model2[[1]] 132 -24049.02 o$model2[[2]]   60 -11074.95 o$model2[[3]]   32 -26662.86
```{r}

# need squared term for flow or temp?
mod[[3]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * tempStd2 + 
                   isYOY * river * season * flowStd2  +
                   (1|ind) + (1|season), data = df ) }

mod[[4]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * tempStd2 * flowStd2  +
                   (1|ind) + (1|season), data = df ) }

mod[[5]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * tempStd2 + 
                   (1|ind) + (1|season), data = df ) }

mod[[6]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * flowStd2  +
                   (1|ind) + (1|season), data = df ) } 
# keep out squared terms for now
```

        rowname  df       AIC     rowname.1 df.1     AIC.1     rowname.2 df.2     AIC.2
1 o$model1[[1]] 131 -24064.23 o$model1[[2]]   59 -11091.02 o$model3[[3]]   45 -27221.73
2 o$model2[[1]] 132 -24049.02 o$model6[[2]]   73 -11085.12 o$model4[[3]]   52 -27214.79
3 o$model5[[1]] 163 -23950.60 o$model2[[2]]   60 -11074.95 o$model6[[3]]   38 -26849.65
4 o$model6[[1]] 163 -23862.94 o$model5[[2]]   73 -11045.37 o$model5[[3]]   38 -26825.20
5 o$model4[[1]] 226 -23856.48 o$model3[[2]]   87 -11011.79 o$model1[[3]]   31 -26673.04
6 o$model3[[1]] 195 -23825.07 o$model4[[2]]  101 -10916.61 o$model2[[3]]   32 -26662.86
```{r}
# add species densities?

mod[[7]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * season * cBKTStd +
                   (1|ind) + (1|season), data = df ) }

mod[[8]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY * season * cBNTStd +
                   (1|ind) + (1|season), data = df ) }

mod[[9]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd   +
                   isYOY *         season * cATSStd +
                   (1|ind) + (1|season), data = df ) }

mod[[10]] <- function(df) {
 lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                  isYOY * river * season * cBKTStd +
                  isYOY * river * season * cBNTStd +
                  isYOY *         season * cATSStd +
                  (1|ind) + (1|season), data = df ) }

mod[[11]] <- function(df) {
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * season * cBKTStd * cBNTStd * cATSStd +
                   (1|ind) + (1|season), data = df ) }

mod[[12]] <- function(df) {
  print(c('mod = 12' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * season * cBKTStd * cBNTStd +
                   (1|ind) + (1|season), data = df ) }

# stick with 10 - good for bkt and easiest to code in jags
```

          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
1  o$model10[[1]] 195 -24650.05 o$model12[[2]]   80 -11203.21 o$model11[[3]]   80 -29379.29
2   o$model7[[1]] 139 -24336.63  o$model8[[2]]   66 -11166.73 o$model10[[3]]   52 -28077.66
3  o$model12[[1]] 155 -24316.48  o$model7[[2]]   66 -11129.29 o$model12[[3]]   52 -27717.41
4  o$model11[[1]] 187 -24259.03 o$model10[[2]]   94 -11119.43  o$model7[[3]]   38 -27339.65
5   o$model1[[1]] 131 -24064.23  o$model9[[2]]   66 -11108.18  o$model3[[3]]   45 -27221.73
6   o$model2[[1]] 132 -24049.02  o$model1[[2]]   59 -11091.02  o$model4[[3]]   52 -27214.79
7   o$model8[[1]] 139 -24045.93  o$model6[[2]]   73 -11085.12  o$model6[[3]]   38 -26849.65
8   o$model9[[1]] 139 -24007.57  o$model2[[2]]   60 -11074.95  o$model8[[3]]   38 -26845.97
9   o$model5[[1]] 163 -23950.60 o$model11[[2]]  108 -11049.99  o$model5[[3]]   38 -26825.20
10  o$model6[[1]] 163 -23862.94  o$model5[[2]]   73 -11045.37  o$model9[[3]]   38 -26695.14
11  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
12  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86

@@

# squared density terms?

mod[[13]] <- function(df) {
    print(c('mod = 13' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd2 +

                   (1|ind) + (1|season), data = df ) }

mod[[14]] <- function(df) {
    print(c('mod = 14' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBNTStd2 +

                   (1|ind) + (1|season), data = df ) }

mod[[15]] <- function(df) {
    print(c('mod = 15' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cATSStd2 +
                   (1|ind) + (1|season), data = df ) }

mod[[16]] <- function(df) {
    print(c('mod = 16' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   (1|ind) + (1|season), data = df ) }
```
Keep model16
          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
1  o$model16[[1]] 249 -24778.30 o$model16[[2]]  122 -11211.56 o$model11[[3]]   80 -29379.29
2  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model15[[3]]   59 -28755.46
3  o$model13[[1]] 226 -24689.16 o$model13[[2]]  108 -11167.05 o$model16[[3]]   66 -28318.31
4  o$model10[[1]] 195 -24650.05  o$model8[[2]]   66 -11166.73 o$model14[[3]]   59 -28310.73
5  o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model13[[3]]   59 -28306.10
6   o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model10[[3]]   52 -28077.66
7  o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
8  o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
9   o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
10  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
11  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
12  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
13  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
14  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
15  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
16  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86

@@

#add interaction btw bkt and bnt?
mod[[17]] <- function(df) {
    print(c('mod = 17' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   (1|ind) + (1|season), data = df ) }
```
Keep 17
          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
1  o$model17[[1]] 272 -24796.58 o$model16[[2]]  122 -11211.56 o$model11[[3]]   80 -29379.29
2  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model15[[3]]   59 -28755.46
3  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model16[[3]]   66 -28318.31
4  o$model13[[1]] 226 -24689.16 o$model13[[2]]  108 -11167.05 o$model17[[3]]   73 -28313.67
5  o$model10[[1]] 195 -24650.05  o$model8[[2]]   66 -11166.73 o$model14[[3]]   59 -28310.73
6  o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model13[[3]]   59 -28306.10
7   o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model10[[3]]   52 -28077.66
8  o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
9  o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
10  o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
11  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
12  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
13  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
14  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
15  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
16  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
17  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86

```{r}
# add squared flow and temp back in? 
# models with temp or flow squared don't work if have either bnt2 or bkt2 also in model
# test which one to take out with interaction btw cBNT and cBKT in

mod[[18]] <- function(df) {
    print(c('mod = 18' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                 #  isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   (1|ind) + (1|season), data = df ) }

mod[[19]] <- function(df) {
    print(c('mod = 19' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                   isYOY * river * season * cBKTStd2 +
                 #  isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   (1|ind) + (1|season), data = df ) }

mod[[20]] <- function(df) {
    print(c('mod = 20' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                 #  isYOY * river * season * cBKTStd2 +
                  # isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   (1|ind) + (1|season), data = df ) }
```
Take out bkt2, for models >20
          rowname  df       AIC      rowname.1 df.1     AIC.1      rowname.2 df.2     AIC.2
1  o$model17[[1]] 272 -24796.58 o$model18[[2]]  122 -11217.98 o$model11[[3]]   80 -29379.29
2  o$model18[[1]] 241 -24795.12 o$model16[[2]]  122 -11211.56 o$model15[[3]]   59 -28755.46
3  o$model16[[1]] 249 -24778.30 o$model17[[2]]  136 -11207.54 o$model16[[3]]   66 -28318.31
4  o$model14[[1]] 218 -24767.67 o$model12[[2]]   80 -11203.21 o$model17[[3]]   73 -28313.67
5  o$model19[[1]] 249 -24730.67 o$model20[[2]]  108 -11169.43 o$model14[[3]]   59 -28310.73
6  o$model20[[1]] 218 -24727.16 o$model13[[2]]  108 -11167.05 o$model13[[3]]   59 -28306.10
7  o$model13[[1]] 226 -24689.16  o$model8[[2]]   66 -11166.73 o$model19[[3]]   66 -28282.69
8  o$model10[[1]] 195 -24650.05 o$model19[[2]]  122 -11146.57 o$model18[[3]]   66 -28267.13
9  o$model15[[1]] 210 -24589.74 o$model14[[2]]  108 -11140.80 o$model10[[3]]   52 -28077.66
10  o$model7[[1]] 139 -24336.63  o$model7[[2]]   66 -11129.29 o$model20[[3]]   59 -28017.53
11 o$model12[[1]] 155 -24316.48 o$model10[[2]]   94 -11119.43 o$model12[[3]]   52 -27717.41
12 o$model11[[1]] 187 -24259.03  o$model9[[2]]   66 -11108.18  o$model7[[3]]   38 -27339.65
13  o$model1[[1]] 131 -24064.23  o$model1[[2]]   59 -11091.02  o$model3[[3]]   45 -27221.73
14  o$model2[[1]] 132 -24049.02  o$model6[[2]]   73 -11085.12  o$model4[[3]]   52 -27214.79
15  o$model8[[1]] 139 -24045.93  o$model2[[2]]   60 -11074.95  o$model6[[3]]   38 -26849.65
16  o$model9[[1]] 139 -24007.57 o$model11[[2]]  108 -11049.99  o$model8[[3]]   38 -26845.97
17  o$model5[[1]] 163 -23950.60  o$model5[[2]]   73 -11045.37  o$model5[[3]]   38 -26825.20
18  o$model6[[1]] 163 -23862.94 o$model15[[2]]  108 -11030.68  o$model9[[3]]   38 -26695.14
19  o$model4[[1]] 226 -23856.48  o$model3[[2]]   87 -11011.79  o$model1[[3]]   31 -26673.04
20  o$model3[[1]] 195 -23825.07  o$model4[[2]]  101 -10916.61  o$model2[[3]]   32 -26662.86

```{r}
mod[[21]] <- function(df) {
    print(c('mod = 21' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                 #  isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   isYOY * river * season * tempStd2 +

                   (1|ind) + (1|season), data = df ) }

mod[[22]] <- function(df) {
    print(c('mod = 22' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                #   isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   isYOY * river * season * flowStd2 +
                   (1|ind) + (1|season), data = df ) }

mod[[23]] <- function(df) {
    print(c('mod = 23' ))
  lmer( grLength ~ isYOY * river * season * tempStd * flowStd  +
                   isYOY * river * season * cBKTStd +
                   isYOY * river * season * cBNTStd +
                   isYOY *         season * cATSStd +
                #   isYOY * river * season * cBKTStd2 +
                   isYOY * river * season * cBNTStd2 +
                   isYOY * river * season * cBNTStd * cBKTStd +
                   isYOY * river * season * tempStd2 +
                   isYOY * river * season * flowStd2 +
                   (1|ind) + (1|season), data = df ) }
